On the power of conditional independence testing under model-X \support{EK was partially supported by NSF DMS-2113072.}

### 2022-11-21 publication/crtpower-ejs.tex
Put authors on different lines

\begin{aug}
\author{\fnms{Eugene} \snm{Katsevich}\ead[label=e1]{ekatsevi@wharton.upenn.edu}}
\and
\author{\fnms{Aaditya} \snm{Ramdas}\ead[label=e2]{aramdas@stat.cmu.edu}}

\address{Department of Statistics and Data Science, University of Pennsylvania\\
Department of Statistics and Data Science, Carnegie Mellon University\\
Machine Learning Department, Carnegie Mellon University \\
\printead{e1,e2}}
\runauthor{Katsevich and Ramdas}

>>>>

\begin{aug}
\author{\fnms{Eugene} \snm{Katsevich}\ead[label=e1]{ekatsevi@wharton.upenn.edu}}
\address{Department of Statistics and Data Science, University of Pennsylvania \\
\printead{e1}}

\author{\fnms{Aaditya} \snm{Ramdas}\ead[label=e2]{aramdas@stat.cmu.edu}}
\address{Department of Statistics and Data Science, Carnegie Mellon University\\
Machine Learning Department, Carnegie Mellon University \\
\printead{e2}}

\runauthor{Katsevich and Ramdas}
